Synthesis of Rules for Network Intrusion Detectors

### 2019-10-24 paper/paper.tex
pass

\tname{} leverages public datasets\cite{tcpreplay} of negative traffic
to guide the search for more general rules, hence addressing the
overffiting issue. The goal of this step is to create rules that
captures traffic similar to the input malicious traffic. To achieve
that goal, \tname{} \emph{minimizes} the rules produced in the
previous step, preserving the invariant of \emph{only} capturing the
positive malicious traffic. A rule is minimal if discarding any option
results in capturing negative (\ie{}, benign) traffic.  The
minimization procedure we propose in this step builds on the
observation that all options from the rule produced in the previous
step are satisifed by the positive traffic. Consequently, any subset
of these options also captures the positive traffic. The procedure
iteratively discards options from the candidate rule until it detects
that the rule is minimal, \ie{}, it finds that no other options can be
removed. The procedure uses negative traffic to guide the search.

\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\algnewcommand\And{\textbf{and} }
\begin{algorithm}[t!]
\textbf{INPUT:} overconstrained rule $or$ \\
\textbf{OUTPUT:} Set of minimal rules $\mathcal R$\\
\vspace{-3ex}
\captionof{algorithm}{Minimization algorithm}\label{algo1}
\begin{algorithmic}[1]
  \State $\mathcal R \gets \{\mathit{or}\}$\Comment{initial population
    of candidate solutions contains only the input rule.}\label{line-init}
  \Do\label{start-do-while}
      \State $\mathcal R' \gets \emptyset$\Comment{starting new
        iteration. new generation should be empty.}\label{init-rprime}
      \ForEach {$ro \in \mathcal R $}\Comment{analyze each candidate individual/rule separately.}\label{start-foreach}
           \For {$i \gets 1$ to $N$}\Comment{mutate each rule $N$ times.}
               \State $r \gets copy(ro)$      
               \State $j\gets \mathit{rand}(0,\mathit{len}(r))$
               \State $r[j]\gets 0$\Comment{discard option $j$ of rule
                 $r$, acopy of the original rule $\mathit{ro}$}
               \If{$\mathit{isnew}(r)$ \And $\mathit{isfit}(r)$}
                   \State $\mathcal R' \cup\gets \{r\}$\Comment{$r$
                     can lead to a plausible candidate solution.}\label{line-progress}
               \EndIf
           \EndFor
       \EndFor\label{end-foreach}
       \State $\mathcal R \gets R'$\Comment{update new generation}
  \doWhile{$\mathcal R'\not= \{\}$}\Comment{repeat until reaching a fixpoint}\label{end-do-while}
\end{algorithmic}
\end{algorithm}

@@

@@

>>>>

\tname{} leverages public datasets\cite{tcpreplay} of negative traffic
to guide the search for more general rules, hence addressing the
overffiting issue. The goal of this step is to create rules that
captures traffic similar to the input malicious traffic. To achieve
that goal, \tname{} \emph{minimizes} the rules produced in the
previous step, preserving the invariant of \emph{only} capturing the
positive malicious traffic. A rule is minimal if discarding any option
results in capturing negative (\ie{}, benign) traffic.  The
minimization procedure we propose in this step builds on the
observation that all options from the rule produced in the previous
step are satisifed by the positive traffic. Consequently, any subset
of these options also captures the positive traffic. The procedure
iteratively discards options from the candidate rule until it detects
that the rule is minimal, \ie{}, it finds that no other option can be
removed. The procedure uses negative traffic to guide the search.

\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\algnewcommand\And{\textbf{and} }
\begin{algorithm}[t!]
\textbf{INPUT:} overconstrained rule $or$ \\
\textbf{OUTPUT:} Set of minimal rules $\mathcal R$\\
\vspace{-3ex}
\captionof{algorithm}{Minimization algorithm}\label{algo1}
\begin{algorithmic}[1]
  \State $\mathcal R \gets \{\mathit{or}\}$\Comment{initial population
    of candidate solutions contains only the input rule.}\label{line-init}
  \Do\label{start-do-while}
      \State $\mathcal R' \gets \emptyset$\Comment{starting new
        iteration. new generation should be empty.}\label{init-rprime}
      \ForEach {$ro \in \mathcal R $}\Comment{analyze each candidate individual/rule separately.}\label{start-foreach}
           \For {$i \gets 1$ to $N$}\Comment{mutate each rule $N$ times.}\label{start-for}
               \State $r \gets copy(ro)$      
               \State $j\gets \mathit{rand}(0,\mathit{len}(r))$
               \State $r[j]\gets 0$\Comment{discard option $j$ of rule
                 $r$, a copy of the original rule $\mathit{ro}$}
               \If{$\mathit{isnew}(r)$ \And $\mathit{isfit}(r)$}
                   \State $\mathcal R' \cup\gets \{r\}$\Comment{$r$
                     can lead to a plausible candidate solution.}\label{line-progress}
               \EndIf
           \EndFor\label{end-for}
       \EndFor\label{end-foreach}
       \State $\mathcal R \gets R'$\Comment{update new generation}
  \doWhile{$\mathcal R'\not= \{\}$}\Comment{repeat until reaching a fixpoint}\label{end-do-while}
\end{algorithmic}
\end{algorithm}

@@

\begin{theorem}
  The minimization algorithm computes rules that capture only
  the positive traffic.
\end{theorem}
~
\begin{proof}
  Every rule created during the search captures the positive traffic
  as every rule contains a proper subset of the option from the
  original rule and all those options are satisfied by the positive
  traffic. By definition of function $\mathit{isfit}$, these rules
  also capture \emph{only} the positive traffic. If some negative
  traffic was captured, a rule would not be added to $\mathcal
  R'$.\qed
\end{proof}

\begin{proposition}
  The minimization algorithm may not produce minimal rules.
\end{proposition}

The output of the minimization algorithm may contain rules that are
not minimal given the non-determinism of the algorithm. It is possible
that options that could be discarded are not selected in the loop from
lines~\ref{start-for}--\ref{end-for}. However, we found empirically
that a small value of $N$ suffices to produce minimal rules.

@@

\vspace{1ex}
\noindent\textbf{Limitation.} It is worth noting that although
\tname{} is accurate for generating rules that discrimate positive and
negative traffic, the quality of these rules is limited by the quality
of the training data it uses. For the positive traffic, \tname{} only
requires one sample, but can benefit of several samples. For the
negative traffic, \tname{} can use public datasets available online.
